Binary Latent Representations for Efficient Ranking

### 2017-06-14 paper/paper.tex
Exploratory changes.

\section{Related work}
\citet{shrivastava2014asymmetric} propose a solution for efficient ranking of large result sets through approximate maximum inner product search (MIPS). They extend well-known \citep{indyk1998approximate} locality-sensitive hashing techniques to the MIPS setting through asymmetric transformations of the query and candidate vectors, and show their applicability to recommender systems.

Our method is complementary to approximate inner product search. Approximate MIPS proceeds in two stages: (1) identification of candidate result vectors through localicty-sensitive hashing, followed by (2) explicit scoring and sorting of the returned candidates. Replacing real-valued dot products by XNOR operations in the second stage will yield incremental performance gains over a real-valued MIPS approach.

\citet{Shen_2015_ICCV} expand on this approach by learning asymmetric binary hash functions. The hash functions are trained to minimize the L2 norm between the inner product matrix of the original input vectors and the inner product matrix of their binary representations. As a post-processing technique, it is a applicable to a wide range of problems. However, because the binary representations are obtained as a separate step, this approach may not be able to exploit the benefits in training a binary representation approach end-to-end.

>>>>

\section{Complementary and related approaches}
Our work complements rather than replaces existing approaches to efficient ranking through approximate candidate selection.

In particular, binary representations can be used in conjunction with approximate maximum inner product search (MIPS). \cite{shrivastava2014asymmetric} show that well-known locality-sensitive hashing techniques \citep{indyk1998approximate} can be extended to approximate MIPS through asymmetric transformations of the query and candidate vectors, leading to a two-step process whereby candidate vectors are identified through asymmetric hashing

%% \section{Related work}
%% Our model is complementary to methods that focus on restricting the set of candidates that need to be explicitly scored by the ranking system.

%% Our model can be used in conjuction with methods that bound approximate nearest neighbours and maximum inner product approaches
%% Our model is complementary to the chief \citet{shrivastava2014asymmetric} propose a solution for efficient ranking of large result sets through approximate maximum inner product search (MIPS). They extend well-known \citep{indyk1998approximate} locality-sensitive hashing techniques to the MIPS setting through asymmetric transformations of the query and candidate vectors, and show their applicability to recommender systems.

%% Our method is complementary to approximate inner product search. Approximate MIPS proceeds in two stages: (1) identification of candidate result vectors through localicty-sensitive hashing, followed by (2) explicit scoring and sorting of the returned candidates. Replacing real-valued dot products by XNOR operations in the second stage will yield incremental performance gains over a real-valued MIPS approach.

%% \citet{Shen_2015_ICCV} expand on this approach by learning asymmetric binary hash functions. The hash functions are trained to minimize the L2 norm between the inner product matrix of the original input vectors and the inner product matrix of their binary representations. As a post-processing technique, it is a applicable to a wide range of problems. However, because the binary representations are obtained as a separate step, this approach may not be able to exploit the benefits in training a binary representation approach end-to-end.
